---
title: "Appendix Team 3 Quantum_Computing"
output: html_document
author: "Pablo Stockhausen, "
date: '2022-06-26'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

_This R Markdown file will be provided as appendix to the final report of Team 3. Refering this appendix will follow the format of (Appendix I-"outline item of Markdown file"). For example, refering the code of Hypothesis 2 will display as following in the report: (Appendix I-1.2). Please use a browser to interpret the html file._

# 0. Install & import packages

### Install

```{r, warning=FALSE, message=FALSE}
required_packages <- c("tibble", "dplyr", "tidyr", "tidyverse", "igraph", "qgraph", "stringr", "ggplot2", "visNetwork")

to_install_packages <- required_packages[!(required_packages %in% installed.packages()[,"Package"])]

if(length(to_install_packages)) invisible(install.packages(to_install_packages))
```

### Import

```{r, warning=FALSE, message=FALSE}
required_packages <- c("tibble", "dplyr", "tidyr", "tidyverse", "igraph", "qgraph", "stringr", "ggplot2", "visNetwork")

invisible(lapply(required_packages, require, character.only = T))
```

# 1. Data collection & cleaning

---

Data set is given and contains patents regarding quantum computing.

**1.1 Import data**
```{r}
df_qc <- read.csv("Quantum computing.csv", sep=";")
```
---

**1.2 Clean Data**
```{r}
# df_qc gets transformed where each row represents an inventor
df_qc <- df_qc %>% 
  mutate(Inventors=strsplit(Inventors, "\n")) %>% 
  unnest(Inventors)

# df_qc gets transformed where each row represents an applicant in connection with each inventor
df_applicants_qc <- df_qc %>%
  mutate(Applicants=strsplit(Applicants, "\n")) %>% 
  unnest(Applicants)
```

# 2. Create necessary objects

---

**2.1 Create the edge list**
```{r}
edge_list <- df_qc %>%
  select(Inventors, Title, Applicants, No) %>%
  inner_join(., select(., Inventors, No), by="No") %>%
  filter(Inventors.x != Inventors.y) %>%
  unique %>%
  arrange(Title, No)

#rename to columns
names(edge_list)[names(edge_list) == "Inventors.x"] <- "from"
names(edge_list)[names(edge_list) == "Inventors.y"] <- "to"

# replace blanks with _
edge_list$from <- gsub(" ", "_", edge_list$from)
edge_list$to <- gsub(" ", "_", edge_list$to)
edge_list$Applicants <- gsub(" ", "_", edge_list$Applicants)

# Selecting of applicant type is based on the majority of type occurrences
evaluate_knowledge_flow_type <- function(x){
  industrial <- "_INC_|INC_|LLC_|_LLC_|_CORP_|_CORPORATION_"
  academic <- "UNIV_|_UNIV_|INST_|_INST_"
  if(grepl(industrial, x)){
    return("industrial")
  }else{
    if(grepl(academic, x)){
      return("academic")
    }else{
      return("private")
    }
  }
}

edge_list$group <- NA

for (i in 1:nrow(edge_list)){
  row <- edge_list[i,]
  edge_list[i,"group"] <- evaluate_knowledge_flow_type(row$Applicants)
}
```

---

**2.2 Create the edge matrix**
```{r}
unique_nodes <- unique(c(edge_list$from, edge_list$to))
edges_length <- length(unique_nodes)

edge_matrix <- matrix(, nrow = edges_length, ncol = edges_length, dimnames = list(unique_nodes, unique_nodes))

edge_matrix[is.na(edge_matrix)] = 0

for(i in 1:edges_length) {
  prim_inventor <- edge_list[[i,"from"]]
  sec_inventor <- edge_list[[i,"to"]]
  edge_matrix[prim_inventor,sec_inventor] <- edge_matrix[prim_inventor,sec_inventor] + 1 
}

```
---

**2.2 Create the graph object**
```{r}
network_graph <- graph_from_adjacency_matrix(
  edge_matrix,
  mode = "undirected",
  weighted = TRUE
)
```
---

# 3. Network visualization

**3.1 Preview of network graph with fruchtermanreingold Layout**
```{r}
# Use qgraph to plot large graphs
edge_list_from_igraph <- get.edgelist(network_graph,names=FALSE)

qgraph_layout_modified <- qgraph.layout.fruchtermanreingold(edge_list_from_igraph,vcount=vcount(network_graph), area=8*(vcount(network_graph)^2),repulse.rad=(vcount(network_graph)^3.1))

plot(network_graph,layout=qgraph_layout_modified,vertex.size=4,vertex.label=NA)
mtext("Network graph based on fruchtermanreingold layout", side=1)
```

# 4. Answering Hypothesis

---

* **H1: We expect more generalists to adopt the broker role in a network than specialists.**

```{r}
# Measure betweenness centrality for each inventor to determine the brokerage

# Mark who is a broker

# Calculate the Herfindhal index for each inventor

# Evaluate who is a generalist
# (1-H) >= (Top 10% Herfindhal index distribution)

# Evaluate who is a specalist
# (1-H) <=  (Lowest 10% Herfindhal index distribution)

# Connect brokerage and generalist/specialist distribution in final numbers

# Visualize results

```

---

* **H2: We expect that more generalists who adopt the broker role in a network to be of academic origin.**

```{r}
# Use the dataframe from H1

# Determine origin of each inventor | view & use dataframe "edge_list"

# Calculate distribution of identified generalist who are brokers and the applicant type

# Output results in numbers

# Visualize results

```

---

* **H3: We expect peripheral players to be specialists.**

```{r}
# Calculate centrality for each inventor

# Find a percentage of lowest centrality distribution who are the peripheral players

# Get the distribution of generalist/specialist based on the peripheral players

# Output result in numbers

# Visualize results

```