---
title: "Appendix Team 3 Quantum_Computing"
output: html_document
author: "Pablo Stockhausen, "
date: '2022-06-26'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

_This R Markdown file will be provided as appendix to the final report of Team 3. Refering this appendix will follow the format of (Appendix I-"outline item of Markdown file"). For example, refering the code of Hypothesis 2 will display as following in the report: (Appendix I-1.2). Please use a browser to interpret the html file._

# 0. Install & import packages

### Install

```{r, warning=FALSE, message=FALSE}
required_packages <- c("tibble", "dplyr", "tidyr", "tidyverse", "igraph", "qgraph", "stringr", "ggplot2", "visNetwork", "data.table", "centiserve", "reshape2", "remotes", "ggcorrplot")

to_install_packages <- required_packages[!(required_packages %in% installed.packages()[,"Package"])]

if(length(to_install_packages)) invisible(install.packages(to_install_packages, dependencies = TRUE))

remotes::install_github("clementviolet/omnivor")
```

### Import

```{r, warning=FALSE, message=FALSE}
required_packages <- c("tibble", "dplyr", "tidyr", "tidyverse", "igraph", "qgraph", "stringr", "ggplot2", "visNetwork", "data.table", "centiserve", "reshape2", "ggcorrplot")

invisible(lapply(required_packages, require, character.only = T))
```

# 1. Data collection & cleaning

---

Data set is given and contains patents regarding quantum computing.

**1.1 Import data**

```{r}
df_qc <- read.csv("Quantum computing.csv", sep=";")
```

---

**1.2 Clean Data**
```{r}
# Drop Rows where Inventors, Applicants or IPC classes or empty or NA
df_qc <- df_qc[!(is.na(df_qc$IPC) | df_qc$IPC==""), ]
df_qc <- df_qc[!(is.na(df_qc$Inventors) | df_qc$Inventors==""), ]
df_qc <- df_qc[!(is.na(df_qc$Applicants) | df_qc$Applicants==""), ]

# df_qc gets transformed where each row represents an inventor
df_qc <- df_qc %>% 
  mutate(Inventors=strsplit(Inventors, "\n")) %>% 
  unnest(Inventors)

# Clean Inventors & Applicants: Needed to adapt the igraph object cleaning
df_qc$Inventors <- gsub(" ", "_", df_qc$Inventors)
df_qc$Inventors <- gsub("-", ".", df_qc$Inventors)
df_qc$Inventors <- chartr("[]", "..", df_qc$Inventors)
df_qc$Inventors <- chartr("<>", "..", df_qc$Inventors)
df_qc$Applicants <- gsub(" ", "_", df_qc$Applicants)
df_qc$Applicants <- sub("_$", "", df_qc$Applicants)
df_qc$Applicants <- gsub("-", ".", df_qc$Applicants)
df_qc$Applicants <- chartr("[]", "..", df_qc$Applicants)
df_qc$Applicants <- chartr("<>", "..", df_qc$Applicants)

# Replace _ if its last character
df_qc$Inventors <- sub("_$", "", df_qc$Inventors)

# df_qc gets transformed where each row represents an applicant in connection with each inventor
df_applicants_qc <- df_qc %>%
  mutate(Applicants=strsplit(Applicants, "\n")) %>% 
  unnest(Applicants)

```

# 2. Create necessary objects

---

**2.1 Create the edge list**

```{r}
edge_list <- df_qc %>%
  select(Inventors, Title, Applicants, No) %>%
  inner_join(., select(., Inventors, No), by="No") %>%
  filter(Inventors.x != Inventors.y) %>%
  unique %>%
  arrange(Title, No)

# Include the patents, where there is only one author
for (i in 1:nrow(df_qc)){
  row <- df_qc[i,]
  if(sum(df_qc$No == row$No) == 1){
    edge_list[nrow(edge_list) + 1,] <- list(row$Inventors, row$Title, row$Applicants, row$No, row$Inventors)
  }
}

#rename to columns
names(edge_list)[names(edge_list) == "Inventors.x"] <- "from"
names(edge_list)[names(edge_list) == "Inventors.y"] <- "to"

# Selecting of applicant type is based on the majority of type occurrences
identify_applicant_type <- function(x){
  industrial <- "_INC_|INC_|LLC_|_LLC_|_CORP_|_CORPORATION_"
  academic <- "UNIV_|_UNIV_|INST_|_INST_"
  if(grepl(industrial, x)){
    return("industrial")
  }else{
    if(grepl(academic, x)){
      return("academic")
    }else{
      return("private")
    }
  }
}

edge_list$group <- NA

for (i in 1:nrow(edge_list)){
  row <- edge_list[i,]
  edge_list[i,"group"] <- identify_applicant_type(row$Applicants)
}
```

---

**2.2 Create the edge matrix**
```{r}
unique_nodes <- unique(c(edge_list$from, edge_list$to))
edges_length <- length(unique_nodes)

edge_matrix <- matrix(, nrow = edges_length, ncol = edges_length, dimnames = list(unique_nodes, unique_nodes))

edge_matrix[is.na(edge_matrix)] = 0

for(i in 1:edges_length) {
  prim_inventor <- edge_list[[i,"from"]]
  sec_inventor <- edge_list[[i,"to"]]
  edge_matrix[prim_inventor,sec_inventor] <- edge_matrix[prim_inventor,sec_inventor] + 1 
}

rm(list=c("prim_inventor","sec_inventor", "i"))
```

---

**2.2 Create the graph object**
```{r}
network_graph <- graph_from_adjacency_matrix(
  edge_matrix,
  mode = "undirected",
  weighted = TRUE
)
```

---

# 3. Network visualization

**3.1 Preview of network graph with fruchtermanreingold Layout**

```{r}
# Use qgraph to plot large graphs
edge_list_from_igraph <- get.edgelist(network_graph,names=FALSE)

qgraph_layout_modified <- qgraph.layout.fruchtermanreingold(edge_list_from_igraph,vcount=vcount(network_graph), area=8*(vcount(network_graph)^2),repulse.rad=(vcount(network_graph)^3.1))

plot(network_graph,layout=qgraph_layout_modified,vertex.size=4,vertex.label=NA)
mtext("Network graph based on fruchtermanreingold layout", side=1)
```

---

**3.2 Preview of network graph with visNetwork**

```{r}
df_visNetwork <- data.frame(from=edge_list$from, to=edge_list$to)
vis_graph <- graph_from_data_frame(df_visNetwork, directed = FALSE)
vis_data <- toVisNetworkData(vis_graph)
vis_network <- visNetwork(nodes = vis_data$nodes, edges = vis_data$edges)

vis_network %>% 
  visEdges(arrows = list(to = list(enabled= FALSE)), length=30) %>%
  visIgraphLayout(layout = "layout_nicely")
```

# 4. Answering Hypothesis

---

* **H1: We expect more generalists to adopt the broker role in a network than specialists.**

```{r}
# Create data objects that are required for calculations 
df_ipc_qc <- df_qc %>% 
  mutate(IPC=strsplit(IPC, "\n")) %>% 
  unnest(IPC)

df_ipc_qc$IPC <- substring(df_ipc_qc$IPC, 1, 4)

unique_inventors <- unique(df_ipc_qc$Inventors)

df_h1 <- data.frame(Inventor=unique_inventors, Katz_Centr = 1.000000, Betw_Centr = 0, Herf_Index = 0, Herf_Index_ZScore = 0, IsBroker="NotBroker", Diversity_Type="None", Applicant_Type="")

# Measure betweenness centrality for each inventor to determine the brokerage
library(omnivor)
betw_centr <- betweeness_centrality(network_graph, normalized=T) # normalized = T or F --> clarify
df_betw_centr <- data.frame(as.list(betw_centr))
t_df_betw_centr <- transpose(df_betw_centr)
t_df_betw_centr$Inventor <- colnames(df_betw_centr)

for(inventor in unique_inventors){
  sub_df_qc <- df_qc[df_qc$Inventors == inventor, ]
  if(nrow(sub_df_qc) > 1){
    centr <- t_df_betw_centr[t_df_betw_centr$Inventor == inventor, "V1"]
    df_h1[df_h1$Inventor == inventor, "Betw_Centr"] <- centr
  }
}

# We are using Centrality measure by Katz as betweeness centrality gets manipulated by the isolated interconnected patent inventors, with alot of shortest paths. This is way we use a other calculation method that inspect the whole network edges, to have secondary factor for centrality.
# Further we exclude inventors from the brokerage role that only have one patent.
# Centrality measure by Katz
# ...considering all direct connections and also the further interconnections of other actors
# See: Landherr, A., Friedl, B., & Heidemann, J. (2010). A critical review of centrality measures in social networks. Bus Inform Syst Eng 2: 371–385.
katzc <- katzcent(network_graph, vids = V(network_graph), alpha = 0.05)
df_katzc <- data.frame(as.list(katzc))
t_df_katzc <- transpose(df_katzc)
t_df_katzc$Inventor <- colnames(df_katzc)

for(inventor in unique_inventors){
  sub_df_qc <- df_qc[df_qc$Inventors == inventor, ]
  if(nrow(sub_df_qc) > 1){
    centr <- t_df_katzc[t_df_katzc$Inventor == inventor, "V1"]
    df_h1[df_h1$Inventor == inventor, "Katz_Centr"] <- centr
  }
}

# Normalize Columns for visualization purpose
normalization<-function(x){
    return((x-min(x))/(max(x)-min(x)))
}
df_h1$Betw_Centr <- normalization(df_h1$Betw_Centr)
df_h1$Katz_Centr <- normalization(df_h1$Katz_Centr)

# Plot correlation between betweeness centrality and Katz Centrality measure

# Mark who is a broker
for(i in 1:nrow(df_h1)){
  row <- df_h1[i,]
  if((row$Betw_Centr > 0) | (row$Katz_Centr > 0)){
  #if((row$Betw_Centr > 0) & (row$Katz_Centr > 1)){
  #if((row$Betw_Centr > 0)){
    df_h1[df_h1$Inventor == row$Inventor, "IsBroker"] <- "Broker"
  }
}

# Calculate the Herf Index for each inventor
for(inventor in unique_inventors){
  df_ipc_qc_sub <- df_ipc_qc[df_ipc_qc$Inventors == inventor, ]
  ipc_table <- table(df_ipc_qc_sub$IPC)
  total_ipcs <- sum(ipc_table)
  table_as_df <- as.data.frame(ipc_table)
  herf_index <- 0
  for (i in 1:nrow(table_as_df)){
    row <- table_as_df[i,]
    val <- row$Freq
    herf_index <- herf_index + (val / total_ipcs)^2
  }
  df_h1[df_h1$Inventor == inventor, "Herf_Index"] <- herf_index
}

## Plot Herf Index distribution
# Histogram overlaid with kernel density curve
x <- df_h1$Herf_Index
h <- hist(x, main="Distribution of Herfindahl Index", xlab="Herfindahl Index", border="blue", col="green", freq=T, ylab = "Frequency")

xfit <- seq(min(x), max(x), length=40)
yfit <- dnorm(xfit, mean=mean(x), sd=sd(x))
yfit <- yfit * diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)

# Pre calculations before identifying generalists or specialists
# Calculate Z scores
# z score tells you how far a value is from the average of the data in terms of standard deviations.
df_h1 <- df_h1 %>% mutate(Herf_Index_ZScore = (Herf_Index - mean(Herf_Index))/sd(Herf_Index))

# Plot Distribution of Z-Scores
ggplot(df_h1, aes(x = Herf_Index_ZScore)) +
  geom_density() +
  labs(x = "\n Z-Score (z)", y = "Density of (z)", title = "Distribution of (z)\n") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.title.x = element_text(face="bold", colour="brown", size = 12),
        axis.title.y = element_text(face="bold", colour="brown", size = 12))
  
# Evaluate who is a Specialist
# H >= (Top 10% Herfindhal index z-score distribution)
# Calculate top 10%
# P(Z > c) = 0.1 ==> P(Z < c) = 0.9
# use linear interpolation to find nearest values as 0.9 is not present in z table
# For further information, see: https://socratic.org/questions/what-is-the-z-score-corresponding-to-the-top-10-percent-of-any-data-set
nearest_value_z_top10_roof <- 1.29 # Z score for 0.9015, Standard normal table
nearest_value_z_top10_floor <- 1.28 # Z score 0.8997, Standard normal table
nearest_value_p_top10_roof <- 0.9015
nearest_value_p_top10_floor <- 0.8997

top10_way_0.9 <- ((0.9 - nearest_value_p_top10_roof) / (nearest_value_p_top10_floor - nearest_value_p_top10_roof))

z_score_top_10 <- nearest_value_z_top10_roof + ((nearest_value_z_top10_floor - nearest_value_z_top10_roof) * (top10_way_0.9))

cat("Author with a Z-Score over", z_score_top_10, "are evaluated as part of the top 10%.")

for(i in 1:nrow(df_h1)){
  row <- df_h1[i,]
  sub_df_qc <- df_qc[df_qc$Inventors == row$Inventor, ]
  # Include amount of published pantents evaluation of inventor, to avoid inventor that have only published one patent, where no clear IPC classes diversity is observable
  # TODO: CRITICAL OPINION, CHECK
  if((row$Herf_Index_ZScore >= z_score_top_10) & (nrow(sub_df_qc) > 1)){
    df_h1[df_h1$Inventor == row$Inventor, "Diversity_Type"] <- "Specialist"
  }
}


# Evaluate who is a Generalist
# (1-H) <=  (Lowest 10% Herfindhal index distribution)
# No Linear Interpolation needed, as we found exactly 0.1 value
nearest_value_z_lowest10 <- -1.28 # Z score for 0.1003, Standard normal table
nearest_value_p_lowest10 <- 0.1003

lowest10_herf_index <- mean(df_h1$Herf_Index) + ((nearest_value_z_lowest10) * sd(df_h1$Herf_Index))

cat("Author with a Herf-Index under", lowest10_herf_index, "are evaluated as part of the lowest 10%.")

for(i in 1:nrow(df_h1)){
  row <- df_h1[i,]
  sub_df_qc <- df_qc[df_qc$Inventors == row$Inventor, ]
  # Include amount of published patents evaluation of inventor, to avoid inventor that have only published one patent, where no clear IPC classes diversity is observable
  # TODO: CRITICAL OPINION, CHECK
  if((row$Herf_Index <= lowest10_herf_index) & (nrow(sub_df_qc) > 1)){
    df_h1[df_h1$Inventor == row$Inventor, "Diversity_Type"] <- "Generalist"
  }
}

# Connect brokerage and generalist/specialist distribution in final numbers
broker_diversity <- df_h1[df_h1$IsBroker == "Broker" & df_h1$Diversity_Type != "None",]

cat("In total", nrow(broker_diversity) ,"brokers with given diversity types were identified.")

table(broker_diversity$Diversity_Type)

cat("From these brokers, we identified 10 Generalists, which equals to a distribution of", (10/nrow(broker_diversity)) * 100, "% \n")
cat("From these brokers, we identified 9 Specialists, which equals to a distribution of", (9/nrow(broker_diversity)) * 100, "%")

# Visualize key players
nodes_groups <- vector()

for (current_node in vis_data$nodes$id){
  if (current_node %in% df_h1$Inventor[df_h1$IsBroker == "Broker"]){
    if(current_node %in% broker_diversity$Inventor){
      nodes_groups <- c(nodes_groups, "Green")
    }else{
      nodes_groups <- c(nodes_groups, "Red")
    }
  }else{
    nodes_groups <- c(nodes_groups, "Black")
  }
}

#vis_data$nodes$group <- nodes_groups 
vis_data$nodes$color <- nodes_groups 

vis_network_2 <- visNetwork(nodes = vis_data$nodes, edges = vis_data$edges, width = "100%")

# Red Nodes = Broker in general
# Green Nodes = Broker with Diversity Type
# Black Nodes = Others
vis_network_2 %>% 
  visPhysics(solver = "forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant = -100, avoidOverlap = 1)) %>%
  visIgraphLayout(layout = "layout_nicely", physics = FALSE, smooth=F)
```

---

* **H2: We expect that more generalists who adopt the broker role in a network to be of academic origin.**

```{r}
# We are continuing using the dataframe from H1.
# Determine origin of each inventor | view & use dataframe "edge_list"
# Selecting of applicant type is based on the majority of type occurrences, see function "identify_applicant_type" in 2.1
df_h2 <- data.frame(from=edge_list$from, to=edge_list$to, group=edge_list$group)

for(i in 1:nrow(df_h1)){
  row <- df_h1[i,]
  df_sub <- df_h2[df_h2$from == row$Inventor, ]
  df_h1[df_h1$Inventor == row$Inventor, "Applicant_Type"] <- names(which.max(table(df_sub$group)))
}

cat("Overall Distribution of applicant types through all Inventors")
table_applicant_type <- table(df_h1$Applicant_Type)
print(table_applicant_type)
df_applicant_type <- as.data.frame(table_applicant_type)
df_applicant_type$Distribution <- df_applicant_type$Freq / sum(df_applicant_type$Freq)

# Calculate distribution of identified generalist who are brokers and the applicant type
generalist_with_applicant_type <- df_h1[df_h1$IsBroker == "Broker" & df_h1$Diversity_Type == "Generalist",]

# Output results in numbers
table(generalist_with_applicant_type$Applicant_Type)

amount_generalists <- nrow(generalist_with_applicant_type)

cat("From", amount_generalists,"generalists, we identified 3 of academic origin, which equals to a distribution of", (3/amount_generalists) * 100, "% \n")
cat("From", amount_generalists,"generalists, we identified 7 of industrial origin, which equals to a distribution of", (7/amount_generalists) * 100, "% \n")

# Draw Conclusion from subset on larger distribution by utilizing correlation factor
pairwise_comp <- df_h1[c(6,7,8)]

pairwise_comp$IsBroker <- factor(pairwise_comp$IsBroker)
pairwise_comp$Diversity_Type <- factor(pairwise_comp$Diversity_Type)
pairwise_comp$Applicant_Type <- factor(pairwise_comp$Applicant_Type)

pairwise_comp <- pairwise_comp[pairwise_comp$IsBroker == "Broker",]

mm <- model.matrix(~ IsBroker + Diversity_Type + Applicant_Type, data=pairwise_comp, contrasts.arg = lapply(pairwise_comp[, sapply(pairwise_comp, is.factor), drop = FALSE], contrasts, contrasts = FALSE))

mm_cor <- cor(mm, use="pairwise.complete.obs", method = c("pearson", "kendall", "spearman"))

colnames(mm_cor) <- c("(Intercept)", "Broker", "NotBroker", "Generalist", "None", "Specialist", "Academic", "Industrial", "Private")
rownames(mm_cor) <- c("(Intercept)", "Broker", "NotBroker", "Generalist", "None", "Specialist", "Academic", "Industrial", "Private")

mm_cor %>% ggcorrplot(show.diag = F, type = "lower", lab=TRUE, lab_size=2.5)

cat("Correlation of Generalist and Academic is 0.14, given that the inspected inventors are brokers.")
cat("Correlation of Generalist and Industrial is -0.12, given that the inspected inventors are brokers.")

print("Despite the measurement of 10 generalists, where 3 inventors are of academic origin, the overall correlation factor of generalist in combination with academic is higher.")

```

---

* **H3: We expect peripheral players to be specialists.**

```{r}
# Calculate centrality for each inventor

# Find a percentage of lowest centrality distribution who are the peripheral players

# Get the distribution of generalist/specialist based on the peripheral players

# Output result in numbers

# Visualize results

```